RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-18 paper.tex
fix typo
screenshot for teaser
vismashup and crowdlabs

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  %% \includegraphics[width=.9\linewidth]{figs/teaser.jpg}
  % \vspace{-.5em}
  \caption{We'll tease you.
  }
% \vspace{-.5em}
}

@@

\todo{Define the requirements for the system}
\begin{itemize}
\item Technology transfer. Things developed by analysts need to become accessible in the production environment and should be supported in the environment, making it easy to push new features, experiments, etc.
\item Dasboarding. There should be a mode in which people can operate the experiments without coding. At times code has to be written because some things cannot be done any other way but other people must not ever see code because their eyes will fall out.
\item Version control as a primary concept in the repository. Need to control the visibility of 
\item Modern interactive technologies. People want to interact with data to explore it. Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
\item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agarwala design considerations for collaborative visual analytics.
\end{itemize}

@@

VisMashup
\cite{Santos:2009:VST}

Crowdlabs
\cite{Mates:2011:CSA}

@@

\begin{figure}
\hspace{-0.08\linewidth}
\includegraphics[width=1.1\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture}
\end{figure}

>>>>

%% Uncomment below to include a teaser figure.
\teaser{
  \centering
  \includegraphics[width=.3\linewidth]{fig/screenshots/wdcplotsmall.jpg}
  %% \includegraphics[width=.9\linewidth]{figs/teaser.jpg}
  % \vspace{-.5em}
  \caption{Left: RCloud integration of HTML5 visualization libraries such
    as D3~\cite{Bostock:2011:DDD} and Crossfilter~\cite{Square:2014:CFM}.
  }
% \vspace{-.5em}
}

@@

\todo{Define the requirements for the system}
\begin{itemize}
\item Technology transfer. Things developed by analysts need to become accessible in the production environment and should be supported in the environment, making it easy to push new features, experiments, etc.
\item Dasboarding. There should be a mode in which people can operate the experiments without coding. At times code has to be written because some things cannot be done any other way but other people must not ever see code because their eyes will fall out.
\item Version control as a primary concept in the repository. Need to control the visibility of 
\item Modern interactive technologies. People want to interact with data to explore it. Scalable technologies like crossfilter exist. Want to support those in the context of an R environment. Need to support full 2-way communication between computing in the cloud and interaction on the web.
\item Other requirements e.g. Kandel's user study. Not our contribution but things we must address, mentioned in related work section. Heer/Agrawala design considerations for collaborative visual analytics.
\end{itemize}

@@

VisMashup~\cite{Santos:2009:VST} and Crowdlabs~\cite{Mates:2011:CSA}
are tools built on top of the VisTrails workflow management
system~\cite{Callahan:2006:VVM}. VisMashup defines a schema and
semantics for automatically deriving user interfaces from workflows,
while Crowdlabs exposes these capabilities on a website feature
workflow upload and remote execution. In our view, the impedance
mismatch between a dataflow pipeline specification and the power of a
general-purpose language is too great for the type of general
exploratory work in data science teams. As a result, RCloud tries to
provide a closer data-analysis to analysts accustomed to createing and
executing R and Python code while keeping many of the attractive
properties like automatic versioning and management.

@@

\begin{figure}
\includegraphics[width=\linewidth]{fig/system/system.pdf}
\caption{\label{fig:system}A diagram of RCloud's architecture}
\end{figure}
